### 2018-02-05 README.Rmd
update readme example

# simulate simple data structure
set.seed(1234)
n <- 200
W <- data.frame(W1 = runif(n,-2,2), W2 = rbinom(n,1,0.5))
A <- rbinom(n, 1, plogis(-2 + W$W1 - 2*W$W2))
Y <- rbinom(n, 1, plogis(-2 + W$W1 - 2*W$W2 + A))

@@

# get confidence intervals for marginal means
ci_fit1 <- ci(fit1)
# print the output
ci_fit1

# get confidence intervals for ate
ci_ate1 <- ci(fit1,contrast = c(-1, 1))
# print the output
ci_ate1
```

>>>>

# simulate simple data structure
set.seed(12345)
n <- 200
W <- data.frame(W1 = runif(n,-2,2), W2 = rbinom(n,1,0.5))
A <- rbinom(n, 1, plogis(-2 + W$W1 - 2*W$W1*W$W2))
Y <- rbinom(n, 1, plogis(-2 + W$W1 - 2*W$W1*W$W2 + A))

@@

# get confidence intervals for marginal means
# truth is E[Y(1)] = 0.29, E[Y(0)] = 0.15
ci_fit1 <- ci(fit1)
# print the output
ci_fit1

# get confidence intervals for ate
# truth is E[Y(1)] - E[Y(0)] = 0.14
ci_ate1 <- ci(fit1, contrast = c(-1, 1))
# print the output
ci_ate1
```
